A spectacular title

### 2018-09-28 Project2/Project2.tex

\section{Method}
\label{sec:method}

>>>>

\section{Method}
\label{sec:method}
\subsection{Buckling beam}
Considering a beam that is fastened in both ends which moves up and down when a force F is exerted on it can be described by a differential equation
%
\begin{gather}
    \gamma \frac{d²u(x)}{dx²} = -Fu(x),
\end{gather}
%
where $u(x)$ is the displacement of the beam in the y-direction and $\gamma$ is a constant that is defined by the properties of the beam, such as the rigidity. Since the beam is fastened in both ends, the displacement $u(x) = 0$ and the sum outer forces on the beam is zero.
